Dominance Regions for Rank Two Cluster Algebras

### 2022-05-16 dominance_regions.tex
edit in section 7

  \begin{remark}
    Observe that $S_{\bfa,r}$ can be expressed in terms of monomial symmetric functions evaluated at $\bfa$ as $\frac{m_{2^{(r)},1^{(n-2r)}}}{m_{1^{(n)}}}$.
    Analogous expansions of $x_{(n,-n)}^{\bfa}$ in terms of triangular or greedy basis elements lead to Schur functions or elementary symmetric functions evaluated at $\bfa$ as $\frac{s_{2^{(r)},1^{(n-2r)}}}{s_{1^{(n)}}}$ and $\frac{e_{r,n-r}}{e_n}$, respectively.
    We leave the details to the interested reader.
  \end{remark}

>>>>

  \begin{remark}
    Observe that the expansion coefficients $S_{\bfa,r}$ can be expressed in terms of monomial symmetric functions evaluated at $\bfa$ as $\frac{m_{2^{(r)},1^{(n-2r)}}}{m_{1^{(n)}}}$.
    Analogous expansions of $x_{(n,-n)}^{\bfa}$ in terms of triangular or greedy basis elements lead to Schur functions or elementary symmetric functions evaluated at $\bfa$ as $\frac{s_{2^{(r)},1^{(n-2r)}}}{s_{1^{(n)}}}$ and $\frac{e_{r,n-r}}{e_n}$, respectively.
    We leave the details to the interested reader.
  \end{remark}
